Growth model analysis

### 2018-06-25 manuscriptAnalysis/MS_Analysis.Rmd
with good long runs

mcmc <- list()
load("D:/projects/linkedModels/data/out/dG_1528425682_bkt1997_Nimble.RData")

@@

load("D:/projects/linkedModels/data/out/dG_1528410796_bnt1997_Nimble.RData")
mcmc[['bnt']]  <- mcmcProcessed

load("D:/projects/linkedModels/data/out/dG_1528735018_ats1997_Nimble.RData")
mcmc[['ats']]  <- mcmcProcessed

@@

len %>% filter(ind == 1, !firstObs, iter%%50==0) %>%
  ggplot(aes(obs,est)) +
  geom_point() +
  geom_line(aes(group = iter)) +
  geom_point(aes(obs,estMean), color='red', size=3) +
  geom_point(aes(obs,observedLen), color='blue', size=3)

@@

rHat <- list()
rHat[['bkt']] <- array2df(mcmc[['bkt']]$Rhat$grBeta, levels = list(beta=1:5,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="rHat")
rHat[['bnt']] <- array2df(mcmc[['bnt']]$Rhat$grBeta, levels = list(beta=1:5,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="rHat")
rHat[['ats']] <- array2df(mcmc[['ats']]$Rhat$grBeta, levels = list(beta=1:4,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="rHat")

@@

ggplot(rHat[[3]], aes(beta,rHat)) +
  geom_point() +
  facet_grid(river+isYOY~season)

>>>>

mcmc <- list()
load("D:/projects/linkedModels/data/out/dG_1529763682_bkt1997_Nimble.RData")

@@

load("D:/projects/linkedModels/data/out/dG_1529720799_bnt1997_Nimble.RData")
mcmc[['bnt']]  <- mcmcProcessed

load("D:/projects/linkedModels/data/out/dG_1529778009_ats1997_Nimble.RData")
mcmc[['ats']]  <- mcmcProcessed

@@

len %>% filter(ind == 20, !firstObs, iter%%50==0) %>%
  ggplot(aes(obs,est)) +
  geom_point() +
  geom_line(aes(group = iter)) +
  geom_point(aes(obs,estMean), color='red', size=3) +
  geom_point(aes(obs,observedLen), color='blue', size=3)

@@

rHat <- list()
rHat[['bkt']] <- array2df(mcmc[['bkt']]$Rhat$grBeta, levels = list(beta=1:4,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="rHat")
rHat[['bnt']] <- array2df(mcmc[['bnt']]$Rhat$grBeta, levels = list(beta=1:4,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="rHat")
rHat[['ats']] <- array2df(mcmc[['ats']]$Rhat$grBeta, levels = list(beta=1:4,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="rHat")

@@

ggplot(rHat[[1]], aes(beta,rHat)) +
  geom_point() +
  facet_grid(river+isYOY~season)
